# SileR

This is the GitHub repository hosting the R package SileR. The package will not
evolve much in the future because it aims at documenting how we obtained the
results for the paper entitled "Differences in age-specific mortality
between wild-caught and captive-born Asian elephants" by Khyne U Mar,
Mirkka Lahdenperä, Alexandre Courtiol and Virpi Lummaa (in review).
The only planned updates are those that will be necessary to maintain
compatibility with other packages, so that our code won't break.

The main goal of the R package SileR is to fit survival models derived from a
model introduced by Siler ("A competiting-risk model
for animal mortality", Ecology, 1979). The main differences are that the
effect of covariate(s) are being investigated and that the survival models
have to be fited on right and left censored longitudinal data.

This package has not been conceived for general use. It serves to document the
steps of our analysis.

## Installation

1. make sure you have the tools allowing to compile R packages on your computer:

* if you are using Linux, you should already have them.

* if you are using MacOS, you need to install Xcode (available from https://developer.apple.com/xcode/) if you have not done it.

* if you are using Windows, you need to install Rtools (available from https://cran.r-project.org/bin/windows/Rtools/) if you have not done it.

2. install the R package ```drat``` (only if you don't have it):

```{r, eval = FALSE}
install.packages("drat")
```

3. install the R package SileR:

```{r, eval = FALSE}
drat::addRepo("courtiol")
install.packages("SileR")
```

## Usage

1. load the package:

```{r, eval = FALSE}
library("SileR")
```

2. access the main documentation by typing:

```{r, eval = FALSE}
help("SileR")
```

## How to explore the sources of the package?

You can either browse the file above within GitHub or download the *.tar.gz file containing the sources.
This file is available here: https://github.com/courtiol/drat/blob/gh-pages/src/contrib/SileR_0.2.tar.gz
