# SileR

This is the GitHub repository hosting the R package SileR. The package will not
evolve much in the future because it aims at documenting how we obtained the
results for the paper entitled "Differences in age-specific mortality
between wild-caught and captive-born Asian elephants" by Khyne U Mar,
Mirkka Lahdenperä, Alexandre Courtiol and Virpi Lummaa (in review).
The only planned updates are those that will be necessary to maintain
compatibility with other packages, so that our code won't break.

The main goal of the R package SileR is to fit survival models derived from a
model introduced by Siler ("A competiting-risk model
for animal mortality", Ecology, 1979). The main differences are that the
effect of covariate(s) are being investigated and that the survival models
have to be fited on right and left censored longitudinal data.

This package has not been conceived for general use. It serves to document the
steps of our analysis.

## Installation

1. install the R package ```drat``` (only if you don't have it):

```{r, eval = FALSE}
install.packages("drat")
```

2. install the R package SileR:

```{r, eval = FALSE}
drat::addRepo("courtiol")
install.packages("SileR")
```

## Usage

1. load the package:

```{r, eval = FALSE}
library("SileR")
```

2. access the main documentation by typing:

```{r, eval = FALSE}
help("SileR")
```

